---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Here is an example of using `biker`:

```{r, echo=FALSE, results='asis'}
library(bikesR)
ans1 = loadBikes(range = '05Jul2017-11Jul2017')
knitr::kable(head(ans1$hourlyRentals, 10))
```

There are several outputs from the load data function, some of which can be fitted using the internal function fit.

You can fit and plot the data using loess, splines, arima.


```{r}
ans2 = fit(ans1, data_type = 'hourlyRentals', fit_type = 'smooth.spline')
plot(ans2)
ans3 = fit(ans1, data_type = 'dailyRentals', fit_type = 'loess')
plot(ans3)
ans4 = fit(ans1, data_type = 'hourlyRentals', fit_type = 'arima')
plot(ans4)
```

loess and smoothing splines function calls allow you to pass in smoothing parameters
```{r}
ans2 = fit(ans1, data_type = 'hourlyRentals', fit_type = 'smooth.spline', spar = 0.5)
# plot(ans2)
ans3 = fit(ans1, data_type = 'dailyRentals', fit_type = 'loess', span = 5)
# plot(ans3)

```

Others are used for exploratory data analysis and can also be plotted on spatial visualisations.
```{r}
knitr::kable(head(ans1$stationStats, 10))
map.biker(obj = ans1, data_type = 'stationStats', 'usage')
map.biker(obj = ans1, data_type = 'stationStats', 'rentals')

```

Included in the package, is a data set called station_locations, which contains all current bike stations and longitude and latitude coordinates.
```{r}

# knitr::kable(head(ans1$station_locations, 10))
```

This can be used in conjunction with external spatial packages such as ggmap to assist in ad-hoc data analysis of the biker datasets.

```{r}
# require(ggmap)
# # wrapper function for ggmap's route which returns the geocoordinates of the route created by the route function.
# getRoute <- function(df, id){
#   cbind(BikeId = id, route(from = c(as.character(df$StartStationName)),
#    to = c(as.character(df$EndStationName)), mode = 'bicycling'
#    ,structure = "legs"))
# }
# 
# # Lets trace the journey of a single bike over the course of the week
# sample = getRoute(ans1$data, id = 1)
# # get potential routes between each station the bike has visited
# map <- get_map(location = 'London', zoom = 14)
# ggmap(map, base_layer = ggplot(aes(x = endLon, y = endLat),data = sample)) + 
#   geom_leg(data = sample,
#          aes(x = startLon, y = startLat, xend = endLon, yend = endLat),
#          alpha = 3/4, size = 2  ) + 
#   labs(x = 'Longitude', y = 'Latitude') + 
#   ggtitle("Journey of a bike over the course of a week")
```



```{r, echo=FALSE, results='asis'}
knitr::kable(head(ans1$hourlyRentals, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
