---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Here is an example of using `biker`:

```{r, echo=FALSE, results='asis'}
library(bikesR)
ans1 = loadBikes(range = '26Jul2017-31Jul2017')
knitr::kable(head(ans1$hourlyRentals, 10))
```

There are several outputs from the load data function, some of which can be fitted using the internal function fit.

You can fit and plot the data using loess, splines, arima

```{r}
ans2 = fit(ans1, data_type = 'hourlyRentals', fit_type = 'smooth.spline')
plot(ans2)
ans3 = fit(ans1, data_type = 'dailyRentals', fit_type = 'loess')
plot(ans3)
ans4 = fit(ans1, data_type = 'hourlyRentals', fit_type = 'arima')
plot(ans4)
```


Others are used for exploratory data analysis and can also be plotted on spatial visualisations.
```{r}
knitr::kable(head(ans1$stationStats, 10))
map.biker(obj = ans1, data_type = 'stationStats', 'usage')
map.biker(obj = ans1, data_type = 'stationStats', 'rentals')

```

Included in the package, is a data set called station_locations, which contains all current bike stations and longitude and latitude coordinates.
```{r}
data(station_locations)
knitr::kable(head(station_locations, 10))
```

This can be used in conjunction with external spatial packages such as ggmap to assist in ad-hoc data analysis of the biker datasets.

```{r}
require(ggmap)
# wrapper function for ggmap's route which returns the geocoordinates of the route created by the route function.
getRoute <- function(df, id){
  cbind(BikeId = id, route(from = c(as.character(df$StartStationName)),
   to = c(as.character(df$EndStationName)), mode = 'bicycling'
   ,structure = "legs"))
}

# Lets trace the journey of a single bike over the course of the week
sample = getRoute(ans1$data, id = 1)
# get potential routes between each station the bike has visited
map <- get_map(location = 'London', zoom = 14)
ggmap(map, base_layer = ggplot(aes(x = endLon, y = endLat),data = sample)) + 
  geom_leg(data = sample,
         aes(x = startLon, y = startLat, xend = endLon, yend = endLat),
         alpha = 3/4, size = 2  ) + 
  labs(x = 'Longitude', y = 'Latitude') + 
  ggtitle("Journey of a bike over the course of a week")
```


The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(ans1$hourlyRentals, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
